Training a Gaming Agent on Brainwaves

### 2020-10-12 ErrP.tex
Subo la versión del PDF con todo integrado.  Fijense que el archivo 5-Segments Average.eps ahora se llama avg_5_segments.eps porque a veces chilla Latex si tienen espacios los nombres.  Lo mismo el archivo cross_val (1).eps lo deje con el nombre final de cross_val.eps que era el que tenía originalmente.

\author{Bartolomé Francisco, Moreno Juan,  Navas Natalia, Vitali José, \\
Ramele~Rodrigo,~\IEEEmembership{Member,~IEEE,}
        Santos~Juan~Miguel% <-this % stops a space
\thanks{R. Ramele and J.M.Santos are with the Department
of Computer Engineering, Instituto Tecnológico de Buenos Aires(ITBA), Argentina,
e-mail: rramele@itba.edu.ar.}% <-this % stops a space
\thanks{Manuscript received December 9, 2019; revised August 25, 2020.}}

@@

% make the title area
\maketitle

@@

@@

\begin{figure}[ht]
    \centering
    \includegraphics[scale=0.12]{revisedimages/cross_val.eps}
    \caption{Binary single trial classification score using five different classifiers while recognizing ErrP potentials for the eight OHCs.  The classification score using an ensemble average of 5 epochs is shown as well (GrandAvg). Chance Level is 0.5.}
    \label{fig:classifiers}
\end{figure}

>>>>

\author{
\IEEEauthorblockN{%
  Bartolomé~Francisco\textsuperscript{\textsection}, 
  Moreno~Juan\textsuperscript{\textsection},  
  Navas~Natalia\textsuperscript{\textsection}, 
  Vitali~José\textsuperscript{\textsection}, \\
  Ramele~Rodrigo,~\IEEEmembership{Member,~IEEE,}
  Santos~Juan~Miguel% <-this % stops a space
  }%

\thanks{R. Ramele and J.M.Santos are with the Department
of Computer Engineering, Instituto Tecnológico de Buenos Aires(ITBA), Argentina,
e-mail: rramele@itba.edu.ar.}% <-this % stops a space
\thanks{Manuscript received December 9, 2019; revised August 25, 2020.}}

@@

% make the title area
\maketitle
\begingroup\renewcommand\thefootnote{\textsection}
\footnotetext{Equal contribution}
\endgroup

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.6\textwidth]{revisedimages/avg_closer.eps}
    \includegraphics[width=0.6\textwidth]{revisedimages/avg_further.eps}
    \caption{Grand Average for all OHCs for the closer and further condition.  It can be seen the bump around 300 ms.}
    \label{fig:classifiers}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[scale=0.11]{revisedimages/cross_val.eps}
    \includegraphics[height=40pt,width=1.20\textwidth]{revisedimages/avg_5_segments.eps}
    \caption{Binary single trial classification score using five different classifiers while recognizing ErrP potentials for the eight OHCs.  The classification score using an ensemble average of 5 epochs is shown as well (GrandAvg). Chance Level is 0.5.}
    \label{fig:classifiers}
\end{figure}
